Mendelian randomization for causal inference in Genome-wide association studies

### 2022-01-28 mr-review.Rmd
more refs added
updated table of methods

Horizontal pleiotropy refers to

>>>>

Horizontal pleiotropy refers to the presence of multiple pathways from a genetic 
variant to the outcome. One of these multiple pathways may contain the exposure variable.
The fact that there are multiple pathways from the genetic variant to the outcome violates
the MR assumptions. @verbanck_detection_2018 documented widespread horizontal pleiotropy 
in GWAS. This finding motivated the development of MR-PRESSO and inspired 
further research into methods to accommodate horizontal pleiotropy in MR studies [@verbanck_detection_2018].
* What does MR-PRESSO do? What are its limitations?
